A non-contextual hidden variable model for quantum mechanics

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’
/ ‘finalPaper.tex’

Clearly, entanglement is not necessary to have a
non-multiplicative situation; for instance the
Peres Mermin test is a state independent test
where a separable state can be used to arrive at a
contradiction. On the other hand if everyting is
multiplicative in a situation, can we have
violation of Bell's inequality or non-locality?
The answer is no and therefore, one can say that
Bell's inequalities bring out  non-local
consequences of  non-multiplicative prediction
maps and the notion of non-multiplicativity is
more basic.

In this letter we have presented
non-multiplicativity as an alternative to
contextuality and as an essential signature of
quantumness at the kinematic level. {\color{red} Our result
emphasises the importance of quantum dynamics
to the discussion of contextuality which may have
implications on our model and in general on the
notion of non-multiplicativity.}
%Implications of quantum dynamics for
%our model and in general for the notion of
%non-multiplicativity need to be explored
%further.
We expect this to provide new insights that will be useful
in the areas of foundations of QM and QIP.

>>>>

Clearly, entanglement is not necessary to have a
non-multiplicative situation; for instance the
Peres Mermin test is a state independent test
where a separable state can be used to arrive at a
contradiction. On the other hand if everyting is
multiplicative in a situation, can we have
violation of Bell's inequality or non-locality?
The answer is no and, therefore, one can say that
Bell's inequalities bring out  non-local
consequences of  non-multiplicative prediction
maps and the notion of non-multiplicativity is
more basic.

In this letter we have presented
non-multiplicativity as an alternative to
contextuality and as an essential signature of
quantumness at the kinematic level. {\color{red} Our result
emphasises the importance of quantum dynamics
to the discussion of contextuality which may have
implications on our model and in general on the
notion of non-multiplicativity.}
%Implications of quantum dynamics for
%our model and in general for the notion of
%non-multiplicativity need to be explored
%further.
%We expect this to provide new insights that will be useful
We expect {\color{red}our result} to provide new insights that will be useful
in the areas of foundations of QM and QIP.
